Data Exploration: IUCN and AquaMaps

### 2016-01-14 data_explore/data_explore.Rmd
updated species lists...?

### here are median labels:
scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  annotate(geom = 'text',
           x = area_ratio_quartiles[2], y = 5,
           hjust = 0, vjust = 0,
           color = 'grey50', size = 2,
           fontface = 'bold.italic', angle = 90,
           label = sprintf('Median = %s%%', round(area_ratio_quartiles[2], 1))) +
  annotate(geom = 'text',
           x = 5, y = pct_overlap_quartiles[2],
           hjust = 0, vjust = 0,
           color = 'grey50', size = 2,
           fontface = 'bold.italic', angle = 0,
           label = sprintf('Median = %s%%', round(pct_overlap_quartiles[2], 1)))

@@

>>>>

### here are median labels:
scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  annotate(geom = 'text',
           x = area_ratio_quartiles[2], y = 5,
           hjust = 0, vjust = 0,
           color = 'grey40', size = 2,
           fontface = 'bold.italic', angle = 90,
           label = sprintf('Median = %s%%', round(area_ratio_quartiles[2], 1))) +
  annotate(geom = 'text',
           x = 5, y = pct_overlap_quartiles[2],
           hjust = 0, vjust = 0,
           color = 'grey40', size = 2,
           fontface = 'bold.italic', angle = 0,
           label = sprintf('Median = %s%%', round(pct_overlap_quartiles[2], 1)))

@@

``` {r pct_overlap_vs_ratio_of_area_w_data_poor, echo = FALSE, warning = FALSE, message = FALSE, eval = TRUE}

spp_list <- spp_list %>% mutate(data_poor = ifelse(occurcells < 10, '< 10', '>= 10')
### mongo plot time
scatter_arearatio_vs_overlap <- ggplot(spp_list %>% 
                                         transform(popn_category = reorder(popn_category, category_score)),
                                       aes(x = area_ratio, y = sm_perc, 
                                           color = data_poor,
                                           size = lg_area_pct)) + 
  ggtheme_plot + 
  ### color the quadrant backgrounds:
    annotate("rect", xmin = area_ratio_quartiles[2],  xmax = 100, 
                     ymin = pct_overlap_quartiles[2], ymax = 100, alpha = .3, fill= "green4")  + 
    annotate("rect", xmin = area_ratio_quartiles[2],  xmax =   0, 
                     ymin = pct_overlap_quartiles[2], ymax = 100, alpha = .3, fill= "greenyellow") + 
    annotate("rect", xmin = area_ratio_quartiles[2],  xmax = 100, 
                     ymin = pct_overlap_quartiles[2], ymax =   0, alpha = .3, fill= "orange") + 
    annotate("rect", xmin = area_ratio_quartiles[2],  xmax =   0, 
                     ymin = pct_overlap_quartiles[2], ymax =   0, alpha = .3, fill= "orangered2") + 
  geom_point(alpha = .6)

### Manage scales for color and size 
scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  scale_colour_manual(values = c('>= 10' = 'green4', 
                                 '< 10'  = 'orangered2')) + 
  scale_size_continuous(limits = c(0, 100),
                        breaks = c( 0,    25,    50,    75,    100), 
                        labels = c('0%', '25%', '50%', '75%', '100%')) + 
  scale_x_continuous(expand = c(0, 0), limits = c(0, 100)) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 100))

### here are median labels:
scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  annotate(geom = 'text',
           x = area_ratio_quartiles[2], y = 5,
           hjust = 0, vjust = 0,
           color = 'grey40', size = 2,
           fontface = 'bold.italic', angle = 90,
           label = sprintf('Median = %s%%', round(area_ratio_quartiles[2], 1))) +
  annotate(geom = 'text',
           x = 5, y = pct_overlap_quartiles[2],
           hjust = 0, vjust = 0,
           color = 'grey40', size = 2,
           fontface = 'bold.italic', angle = 0,
           label = sprintf('Median = %s%%', round(pct_overlap_quartiles[2], 1)))

scatter_arearatio_vs_overlap <- scatter_arearatio_vs_overlap +
  labs(x = bquote('Extent alignment '*alpha['ext']*' (%)'), 
       y = bquote('Distribution alignment '*alpha['dist']*' (%)'), 
       title = 'Distribution alignment vs Extent alignment',
       color = 'AM model cells', size = '% ocean range')

ggsave(file.path(dir_fig, 'AreaRatiovsPercOverlap-data_poor.png'), width = 6, height = 3.5)
